---
title: "Descriptive Statistics"
output: html_document
---
country<-tbl(connection, 'country_kpi')
university<-tbl(connection, 'university_kpi')

country%>% explain()
university%>% explain()
```

```{r}
country
university

```

```{r}
countries <- tbl(connection, 'country_kpi') %>% select(1:10) %>% collect()
universities<-tbl(connection, 'university_kpi') %>% select(1:9) %>% collect()


```

#how to select countries 

```{r}

austria <- tbl(connection, 'country_kpi') %>% select(1:10) %>% filter(country_name=="Austria") %>% collect()
netherlands <- tbl(connection, 'country_kpi') %>% select(1:10) %>% filter(country_name=="Netherlands") %>% collect()
germany <- tbl(connection, 'country_kpi') %>% select(1:10) %>% filter(country_name=="Germany") %>% collect()

```

#how to select countries+universities

```{r}
a_uni <- tbl(connection, 'university_kpi') %>% select(1:9) %>% filter(country_name=="Austria") %>% collect()
n_uni <- tbl(connection, 'university_kpi') %>% select(1:9) %>% filter(country_name=="Netherlands") %>% collect()
g_uni <- tbl(connection, 'university_kpi') %>% select(1:9) %>% filter(country_name=="Germany") %>% collect()

```


# transforming the countries dataset

```{r}
countries$countryfact_id<-NULL
countries<-na.omit(countries)
countries$country_name<-factor(countries$country_name)

austria$countryfact_id<-NULL
austria$na.omit(countries)
austria$country_name<-factor(austria$country_name)

netherlands$countryfact_id<-NULL
netherlands$na.omit(countries)
netherlands$country_name<-factor(netherlands$country_name)

germany$countryfact_id<-NULL
germany$na.omit(countries)
germany$country_name<-factor(germany$country_name)

# transforming the universities dataset

universities$unifact_id <- NULL
universities<- na.omit(universities)
universities$country_name<-factor(universities$country_name)

a_uni$unifact_id <- NULL
a_uni<- na.omit(universities)
a_uni$country_name<-factor(a_uni$country_name)

n_uni$unifact_id <- NULL
n_uni<- na.omit(universities)
n_uni$country_name<-factor(n_uni$country_name)

g_uni$unifact_id <- NULL
g_uni<- na.omit(universities)
g_uni$country_name<-factor(g_uni$country_name)

```

#checking for the density amongst for the research variable
```{r}
ggplot(data = universities, aes(x = universities$research, fill = country_name)) + geom_density(col = NA, alpha = 0.35 ) +
  ggtitle("Year")+
  xlab("Research")+
  ylab("Density")
labs(fill = "Country Name")

```

#checking the normality in the countries dataset
```{r}

ggpairs(data=countries, columns=3:10, title="Countries data")
hist(countries$innovation_score)
hist(countries$patent_application)
hist(countries$scientists_and_engineers)
hist(countries$public_rd)
hist(countries$high_citations)
hist(countries$value_added)
hist(countries$education_expenditure)

```
#checking the normality in the universities dataset
```{r}

library(GGally)
ggpairs(data=universities, columns=4:8, title="University data")
hist(universities$teaching)
hist(universities$research)
hist(universities$citations)
hist(universities$industry_income)
hist(universities$international_outlook)

```
# defining a function modeval(X) to calculate the mode of X:
```{r}
library(moments);
modeval = function(X){
  return(as.numeric(names(sort(-table(X))[1])));
}
```
#descriptive stats
```{r}
str(countries)
str(universities)

summary(austria[,4:10])
summary(netherlands[,4:10])
summary(germany[,4:10])

summary(a_uni[,4:8])
summary(n_uni[,4:8])
summary(g_uni[,4:8])


lapply(austria[,4:10], sd)
lapply(nederlands[,4:10], sd)
lapply(germany[,4:10], sd)

lapply(austria[,4:10], var)
lapply(nederlands[,4:10], var)
lapply(germany[,4:10], var)

lapply(a_uni[,4:10], sd)
lapply(n_uni[,4:10], sd)
lapply(g_uni[,4:10], sd)

lapply(a_uni[,4:10], var)
lapply(n_uni[,4:10], var)
lapply(g_uni[,4:10], var)

```


#Multiple Regression Analysis regression for countries dataset
```{r}

trainSize <- round(nrow(countries) * 0.75)
testSize <- nrow(countries) - trainSize

set.seed(123)
training_indices <- sample(seq_len(nrow(countries)),
                           size=trainSize)
trainSet <- countries[training_indices, ]
testSet <- countries[-training_indices, ]
model1 <- lm(formula=trainSet$innovation_score ~ . , data=trainSet)
model2 <- lm(formula=testSet$innovation_score ~ . , data=testSet)

#residual check

ggplot(data=trainSet, aes(model1$residuals)) + 
  geom_histogram(binwidth = 1, color = "black", fill = "purple4") +
  theme(panel.background = element_rect(fill = "white"),
        axis.line.x=element_line(),
        axis.line.y=element_line()) +
  ggtitle("Histogram for Model Residuals") 

ggplot(data=testSet, aes(model2$residuals)) + 
  geom_histogram(binwidth = 1, color = "black", fill = "purple4") +
  theme(panel.background = element_rect(fill = "white"),
        axis.line.x=element_line(),
        axis.line.y=element_line()) +
  ggtitle("Histogram for Model Residuals") 

```

#Multiple Regression Analysis for universities dataset    

```{r}
set.seed(123)
trainSize2 <- round(nrow(uni1) * 0.75)
testSize2 <- nrow(uni1) - trainSize2
training_indices2 <- sample(seq_len(nrow(uni1)),
                            size=trainSize2)
trainSet2 <- uni1[training_indices2, ]
testSet2 <- uni1[-training_indices2, ]

model3 <- lm(formula=trainSet2$international_outlook ~ . , data=trainSet2)

model4 <- lm(formula=testSet2$international_outlook ~ . , data=testSet2)

#residual check

ggplot(data=trainSet2, aes(model3$residuals)) + 
  geom_histogram(binwidth = 1, color = "black", fill = "purple4") +
  theme(panel.background = element_rect(fill = "white"),
        axis.line.x=element_line(),
        axis.line.y=element_line()) +
  ggtitle("Histogram for Model Residuals") 

ggplot(data=testSet2, aes(model4$residuals)) + 
  geom_histogram(binwidth = 1, color = "black", fill = "purple4") +
  theme(panel.background = element_rect(fill = "white"),
        axis.line.x=element_line(),
        axis.line.y=element_line()) +
  ggtitle("Histogram for Model Residuals") 

```
