---
title: "ETL"
output: html_document
---
```{r}
#all our used libraries, make sure to download them!
```{r}
library(RPostgreSQL)
library(tidyverse)
library(dplyr)
library(DBI)
library(readr) #to read the csv file with the data, i.e. read_csv
library(RMySQL) #to put dataframe into database table, i.e. dbWriteTable
```

#Some database connection stuff
#YOU MUST CHANGE THIS --> dbname, host, user, password, maybe other things?
```{r}
db_user <- "postgres"
driver <- dbDriver("PostgreSQL")
connection <- dbConnect(driver, dbname="mypgdb", host="localhost", port=5432, user="postgres", password="password")

```

#Creating the tables, just pretend that there is a star schema ;)
```{sql connection=connection, max.print = 0}
DROP TABLE IF EXISTS country_kpi;
DROP TABLE IF EXISTS university_kpi;

CREATE TABLE country_kpi(
  countryfact_id integer,
  country_name varchar(200),
  year integer,
  innovation_score decimal(18,4),
  patent_application decimal(18,4),
  scientists_and_engineers decimal(18,4),
  public_rd decimal(18,4),
  high_citations decimal(18,4),
  value_added decimal(18,4),
  education_expenditure decimal(18,4)
);

CREATE TABLE university_kpi(
  unifact_id integer,
  uni_name varchar(200),
  country_name varchar(200),
  year integer,
  teaching decimal(18,4),
  research decimal(18,4),
  citations decimal(18,4),
  industry_income decimal(18,4),
  international_outlook decimal(18,4)
);

```
#Saving the csv files with all our data as r variables
#YOU MUST CHANGE THIS --> path to the files
```{r, message=FALSE, warning=FALSE}
country_kpi_tab <- readr::read_csv('C:/Users/Desktop/Business intelligence/Data/country_kpi.csv')
university_kpi_tab <- readr::read_csv('C:/Users//Desktop/Business intelligence/Data/university_kpi.csv')
```

#Populating the database with those r variables
```{r}
dbWriteTable(connection, "country_kpi", country_kpi_tab, append=TRUE, row.names = FALSE)
dbWriteTable(connection, "university_kpi", university_kpi_tab, append=TRUE, row.names = FALSE)
```

#Check out the tables we've just populated!

```{r}
library(RPostgreSQL)
library(tidyverse)
library(dplyr)
library(DBI)
library(readr) #to read the csv file with the data, i.e. read_csv
library(RMySQL) #to put dataframe into database table, i.e. dbWriteTable

#DASHBOARD 
library(devtools)
library(shiny)
library(lattice)
library(rsconnect)
library(shinydashboard)
library(ggplot2)
library(GGally)

#!!! USE THIS TO INSTALL PLOTLY !!!
#devtools::install_github("ropensci/plotly")
library(plotly)
```

#Some database connection stuff
#YOU MUST CHANGE THIS --> dbname, host, user, password, maybe other things?
```{r}
db_user <- "postgres"
driver <- dbDriver("PostgreSQL")
connection <- dbConnect(driver, dbname="mypgdb", host="localhost", port=5432, user="postgres", password="password")

```

#Creating the tables, just pretend that there is a star schema ;)
```{sql connection=connection, max.print = 0}
DROP TABLE IF EXISTS country_kpi;
DROP TABLE IF EXISTS university_kpi;

CREATE TABLE country_kpi(
  countryfact_id integer,
  country_name varchar(200),
  year integer,
  innovation_score decimal(18,4),
  patent_application decimal(18,4),
  scientists_and_engineers decimal(18,4),
  public_rd decimal(18,4),
  high_citations decimal(18,4),
  value_added decimal(18,4),
  education_expenditure decimal(18,4)
);

CREATE TABLE university_kpi(
  unifact_id integer,
  uni_name varchar(200),
  country_name varchar(200),
  year integer,
  teaching decimal(18,4),
  research decimal(18,4),
  citations decimal(18,4),
  industry_income decimal(18,4),
  international_outlook decimal(18,4)
);

```
#Saving the csv files with all our data as r variables
#YOU MUST CHANGE THIS --> path to the files
```{r, message=FALSE, warning=FALSE}
country_kpi_tab <- readr::read_csv('C:/Users/Desktop/Business intelligence/Data/country_kpi.csv')
university_kpi_tab <- readr::read_csv('C:/Users/Desktop/Business intelligence/Data/university_kpi.csv')
```

#Populating the database with those r variables
```{r}
dbWriteTable(connection, "country_kpi", country_kpi_tab, append=TRUE, row.names = FALSE)
dbWriteTable(connection, "university_kpi", university_kpi_tab, append=TRUE, row.names = FALSE)
```
```

